### 2023-08-29 appendix.tex
section

We wish to determine if $q(\textbf{0})$ is reachable in a reset-VASS $V_1$
with
initial configuration $q_0(\textbf{u})$.
To do so, we construct a reset-VASS $V_2$
and an initial configuration $q'_0(\textbf{v})$ 
which is live if and only if 
$q(\textbf{0})$
is reachable from $q_0(\textbf{u})$.

>>>>

We wish to determine if $q(\textbf{0})$ is reachable in a reset-VASS $V_1$
with
initial configuration $q_0(\textbf{u})$.
To do so, we construct a reset-VASS $V_2$
and an initial configuration $q'_0(\textbf{v})$ 
which is live if and only if 
$q(\textbf{0})$
is reachable from $q_0(\textbf{u})$.\alain{in V2 ? préciser tt le temps dans quel vass}
